Efficient pedigree recording for fast population genetics simulation

### 2018-01-21 forwards_paper.tex
a few more words

\begin{figure}
    \begin{center}
        \includegraphics{simplify-state-diagram}
    \end{center}
    \caption{
        A depiction of the state of the simplification algorithm
        at each point in time,
        in the example of Figure~\ref{fig:method_diagram}A.
        Ancestral material from J (red) and K (blue) are traced up through the pedigree
        until they coalesce;
        the smaller colored chromosomes on either side of each solid arrow show the bits inherited from each of the two parental chromosomes;
        each time two colors overlap, a coalescence occurs, and two edges are output.
        For instance, both J and K inherit from H between 0.5 and 0.9,
        which resulted in the first two edges of the simplified table of Figure~\ref{fig:method_diagram}C.
        \label{fig:simplify_state}
    }
\end{figure}

>>>>

\begin{figure}
    \begin{center}
        \includegraphics{simplify-state-diagram}
    \end{center}
    \caption{
        A depiction of the state of the simplification algorithm
        as it moves up through the embellished pedigree
        in the example of Figure~\ref{fig:method_diagram}A.
        Following the ``paint pot'' description in the text,
        we begin by coloring J and K's genomes in red and blue respectively,
        then trace how these colors were inherited back up through the pedigree
        until they coalesce.
        To aid in this,
        the smaller colored chromosomes on either side of each solid arrow
        show the bits inherited from each of the two parental chromosomes,
        with genomic position 0.0 on the bottom and 1.0 at the top.
        Each time a red and a blue segment overlap, a coalescence occurs, two edges are output,
        and we stop propagating that segment.
        For instance, both J and K inherit from H between 0.5 and 0.9,
        which resulted in the first two edges of the simplified table of Figure~\ref{fig:method_diagram}C.
        Later, both inherit from E between 0.2 and 0.5,
        along the paths J-H-G-E and K-I-E respectively,
        resulting in the next two edges.
        \label{fig:simplify_state}
    }
\end{figure}
